### 2017-03-28 intro.tex
Tweaked figure size/pos

\subsection{Designing Simulations}
Beyond the choice of algorithms, the construction of appropriate inital
conditions is also important.  To study large populations of galaxies, along
with large-scale structure, large-volume cosmological boxes with volumes
$\gtrsim 10^6\;\rm{Mpc^3}$, but with spatial resolutions $\sim \rm{kpc}$ are
used (for example, the {\it Illustris} simulations have a softening length of
$1.4\;rm{kpc}$ \citealt{Vogelsberger2014}).  Studying how individual galaxies
form is typically done with cosmological zoom simulations, where a comparatively
cheap dark-matter only simulation is first run to select a region of interest,
which is then resimulated with higher resolution and baryonic physics included
\citep{Navarro1993}. Zoom-in simulations can typically achieve an order of
magnitude or better resolution than full cosmological boxes.  A number of groups
today are using these zoom-in simulations to study the impact of feedback
processes over cosmic time \citep{Stinson2013,Hopkins2014,Agertz2015}.  Isolated
galaxy disc simulations use a constructed disc profiles containing gas and
stars, embedded within a dark halo. These cannot show how galaxies form in a
cosmological environment, but can be run with $\sim \rm{pc}$ resolution to study
closely how internal processes within a galaxy take place
\citep{Hopkins2011,Benincasa2016}.  Details of these internal processes are
discussed in section 1.3.

>>>>

\subsection{Designing Simulations}
Beyond the choice of algorithms, the construction of appropriate inital
conditions is also important.  To study large populations of galaxies, along
with large-scale structure, large-volume cosmological boxes with volumes
$\gtrsim 10^6\;\rm{Mpc^3}$, but with spatial resolutions $\sim \rm{kpc}$ are
used (for example, the {\it Illustris} simulations have a softening length of
$1.4\;\rm{kpc}$ \citealt{Vogelsberger2014b}).  Studying how individual galaxies
form is typically done with cosmological zoom simulations, where a comparatively
cheap dark-matter only simulation is first run to select a region of interest,
which is then resimulated with higher resolution and baryonic physics included
\citep{Navarro1993}. Zoom-in simulations can typically achieve an order of
magnitude or better resolution than full cosmological boxes.  A number of groups
today are using these zoom-in simulations to study the impact of feedback
processes over cosmic time \citep{Stinson2013,Hopkins2014,Agertz2015}.  Isolated
galaxy disc simulations use a constructed disc profiles containing gas and
stars, embedded within a dark halo. These cannot show how galaxies form in a
cosmological environment, but can be run with $\sim \rm{pc}$ resolution to study
closely how internal processes within a galaxy take place
\citep{Hopkins2011,Benincasa2016}.  Details of these internal processes are
discussed in section 1.3.
